Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-05 paper.qmd
Removed long edge parameter

- hexagon bin parameters
    - bottom left bin position $(s_1, \ s_2)$, 
    - the total number of bins ($b$), 
- bin density cutoff, to remove low-density hexagons, and 
- edge length maximum, remove long edges from \gD{} representation.

>>>>

- hexagon bin parameters
    - bottom left bin position $(s_1, \ s_2)$, 
    - the total number of bins ($b$), 
- bin density cutoff, to remove low-density hexagons.
